Log or not - Analysis of ECDC forecasts

### 2022-01-31 analysis/Analysis ECDC forecasts.Rmd
update plots

# plot with mean vs. variance --------------------------------------------------
hub_data |>
  dplyr::select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(location, target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value)) |>
  ggplot(aes(y = var_value, x = mean_value)) +
  geom_point() + 
  facet_wrap(~ target_type, scales = "free") + 
  scale_x_continuous(trans = "log10", labels = label_fn) +
  scale_y_continuous(trans = "log10", labels = label_fn) +
  # scale_x_continuous(labels = label_fn) +
  # scale_y_continuous(labels = label_fn) +
  labs(y = "Variance observed value", x = "Mean observed value") + 
  geom_function(fun = function(x) x^2, linetype = "dashed", size = 0.5) + 
  theme_minimal()

>>>>

# plot with mean vs. variance --------------------------------------------------
hub_data |>
  dplyr::select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(location, target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value)) |>
  ggplot(aes(y = var_value, x = mean_value)) +
  geom_point() + 
  facet_wrap(~ target_type, scales = "free") + 
  scale_x_continuous(trans = "log10", labels = label_fn) +
  scale_y_continuous(trans = "log10", labels = label_fn) +
  # scale_x_continuous(labels = label_fn) +
  # scale_y_continuous(labels = label_fn) +
  labs(y = "Variance observed value", x = "Mean observed value") + 
  geom_function(fun = function(x) x^2, linetype = "dashed", size = 0.5) + 
  theme_minimal() + 
  geom_smooth(alpha = 0.2, size = 0.2)
